Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-09-17 latex/main.tex
Move up the alignment storage and preprocessing bits
remove "accelerated sample matcing" ssection

LS model \cite{LiStephens2003} is an approximation of the coalescent with recombination
that captures many of the key features of the joint processes of mutation and recombination.
It is widely used in a range of applications in population genetics, including ARG 
% Does Threads use LS?
inference \cite{Kelleher2019,Gunnarsson2024}.
The LS model is an HMM that models a focal genome as a sequence of nucleotides (i.e. the observed states),
which are probabilistically emitted as an imperfect mosaic of a set of genomes in a reference panel (i.e., the hidden states).
The process of switching between the genomes in the reference panel is governed by a transition matrix,
and mismatches between a focal genome and a genome of the reference panel (from which it is ``copied'') are permitted as emissions.

@@

\subsubsection*{Accelerating sample matching}

>>>>

The LS model \cite{LiStephens2003} is an approximation of the coalescent with recombination
that captures many of the key features of the joint processes of mutation and recombination.
It is widely used in a range of applications in population genetics, including ARG 
% Does Threads use LS?
inference \cite{Kelleher2019,Gunnarsson2024}.
The LS model is an HMM that models a focal genome as a sequence of nucleotides (i.e. the observed states),
which are probabilistically emitted as an imperfect mosaic of a set of genomes in a reference panel (i.e., the hidden states).
The process of switching between the genomes in the reference panel is governed by a transition matrix,
and mismatches between a focal genome and a genome of the reference panel (from which it is ``copied'') are permitted as emissions.

@@
